### 2019-01-16 README.Rmd
update pkgdown with candidate hex
spellcheck
The dev version of the `spelling` package now spellchecks README and NEWS

@@

RNeXML: The next-generation phylogenetics format comes to R
=====================================================

@@

Although the published version of the article is paywalled, the source of the manuscript, and a much better rendered PDF, are included in this package (in the `manuscripts` folder). You can also find it [freely available on arXiv](http://arxiv.org/abs/1506.02722).

>>>>

# RNeXML  <img src="man/figures/logo.svg" align="right" alt="" width="120" />

@@

@@

Although the published version of the article is pay-walled, the source of the manuscript, and a much better rendered PDF, are included in this package (in the `manuscripts` folder). You can also find it [freely available on arXiv](http://arxiv.org/abs/1506.02722).
